Temporal graph realization from fastest paths

### 2024-03-31 SAND2024/SAND24-cameraReady.tex
Camera ready SAND24 submitted
Final camera ready version

\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversiondetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g. Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional

@@

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction. 
To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting. However, many other connectivity-related problems have been studied in the temporal setting~\cite{Mertzios-transitivity21,Akrida-explorer-21,enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22,FuchsleMNR22,KMZ23}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.

@@

%\subparagraph{Further problem variants.}
There are many natural variants of our problem that are well-motivated and warrant consideration. 
%In the following, we give two specific examples. 
We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period. A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations. 
%Our work gives a starting point for many interesting future research directions such as the two mentioned examples.

>>>>

\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversiondetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g. Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
\relatedversiondetails{Full Version}{https://arxiv.org/abs/2302.08860}

@@

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{Arnaud Casteigts and Fabian Kuhn}
\EventNoEds{2}
\EventLongTitle{3rd Symposium on Algorithmic Foundations of Dynamic Networks (SAND 2024)}
\EventShortTitle{SAND 2024}
\EventAcronym{SAND}
\EventYear{2024}
\EventDate{June 5-7, 2024}
\EventLocation{Patras, Greece}
\EventLogo{}
\SeriesVolume{292}
\ArticleNo{3}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction. 
To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting. 
Very recently, Erlebach et al.~\cite{ErlebachMW-SAND24} have built upon our results and, among others, studied the case where edges might appear more than once in each period. 
Many other connectivity-related problems have been studied in the temporal setting~\cite{Mertzios-transitivity21,Akrida-explorer-21,enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22,FuchsleMNR22,KMZ23}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.

@@

%\subparagraph{Further problem variants.}
There are many natural variants of our problem that are well-motivated and warrant consideration. 
%In the following, we give two specific examples. 
We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period. A well-motivated variant (especially from the network design perspective) of our problem is to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations. This problem variant has very recently been studied by Mertzios et al.~\cite{MMS24}. 
%Our work gives a starting point for many interesting future research directions such as the two mentioned examples.

### 2024-03-31 SAND2024/SAND24-longversion.tex
Final camera ready version

\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction. 
To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting. However, many other connectivity-related problems have been studied in the temporal setting~\cite{Mertzios-transitivity21,Akrida-explorer-21,enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22,FuchsleMNR22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.

@@

\subparagraph{Further problem variants.}
There are many natural variants of our problem that are well-motivated and warrant consideration. In the following, we give two specific examples. We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period. A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations. 
%Our work gives a starting point for many interesting future research directions such as the two mentioned examples.

>>>>

\subparagraph{Related work.} Graph realization problems on static graphs have been studied since the 1960s. We provide an overview of the literature in the introduction. 
To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting. 
Very recently, Erlebach et al.~\cite{ErlebachMW-SAND24} have built upon our results and, among others, studied the case where edges might appear more than once in each period. 
Many other connectivity-related problems have been studied in the temporal setting~\cite{Mertzios-transitivity21,Akrida-explorer-21,enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22,FuchsleMNR22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.

@@

\subparagraph{Further problem variants.}
There are many natural variants of our problem that are well-motivated and warrant consideration. In the following, we give two specific examples. We believe that one of the most natural generalizations of our problem is to allow more than one label per edge in every $\Delta$-period. A well-motivated variant (especially from the network design perspective) of our problem would be to consider the entries of the duration matrix $D$ as upper-bounds on the duration of fastest paths rather than exact durations. This problem variant has very recently been studied by Mertzios et al.~\cite{MMS24}.  
%Our work gives a starting point for many interesting future research directions such as the two mentioned examples.
